---
title: "Problem Set #4"
author: "Mike Silva"
date: "2/26/2019"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(janitor)
library(stringr)
library(ggplot2)
library(gt)
```

```{r, include=FALSE}
#load the data
x <- read_csv("ps_4_elections-poll-nc09-3.csv")
```

```{r, include=FALSE}
 #filtered the table to show who did or didn't vote for Democrats and then counted the ones that did with count()
a <- x %>%
  filter(response == "Dem") %>%
  count(TRUE)


b <- x %>%
  #selected response to specify what I was looking at
  select(response) %>% 
  #grouped by response and counted to get numbers associated with each response
  group_by(response) %>% 
  summarise(n=n())

c <- x %>%
 #filtered for when gender observations didn't match gender_combined observations
   filter( gender != gender_combined) %>% 
  #used nrow() to count the difference
  nrow()

d <- x %>% 
  #selected both columns the question discusses
  select(race_eth, file_race_black) %>%
  #used same filter process as last quesiton, this time specifying that race_eth is only showing "white" observations.
  filter(race_eth == "White", race_eth != file_race_black) %>%  
  nrow()
d

e <- x %>%
  #narrowed table down to just timestamp and their responses
  select(timestamp, response) %>%
  #arranged the timestamp variable and since I selected response, it shows me what the response was for each timestamp. Then indexed the first and fifth rows which are the first democrat and republican responses.
  arrange(timestamp)

as.numeric((e$timestamp[1] - e$timestamp[5]) * (-1)) %>%
  round()
```


There were `r a$n` respondents who supported the Democratic candidate.

There were `r b$n[3]-b$n[4]` more respondents who favored the Republican candidate than who were Undecided.

There are two gender variables (gender and gender_combined). There are `r c` individuals for whom these variables have different values.

There are `r d` respondents listed as “White” under race_eth who are not listed as “White” under file_race_black.

The first response of Rep came `r as.numeric((e$timestamp[1] - e$timestamp[5]) * (-1)) %>%
  round()` minutes (rounded to the nearest minute) before the first response of Dem.

