---
title: "Problem Set #4"
author: "Mike Silva"
date: "2/26/2019"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(janitor)
library(stringr)
library(ggplot2)
library(gt)
library(tidyr)
```

```{r, include=FALSE}
#load the data
x <- read_csv("ps_4_elections-poll-nc09-3.csv")
```

```{r, include=FALSE}
 #filtered the table to show who did or didn't vote for Democrats and then counted the ones that did with count()
a <- x %>%
  filter(response == "Dem") %>%
  count(TRUE)


b <- x %>%
  #selected response to specify what I was looking at
  select(response) %>% 
  #grouped by response and counted to get numbers associated with each response
  group_by(response) %>% 
  summarise(n=n())

c <- x %>%
 #filtered for when gender observations didn't match gender_combined observations
   filter( gender != gender_combined) %>% 
  #used nrow() to count the difference
  nrow()

d <- x %>% 
  #selected both columns the question discusses
  select(race_eth, file_race_black) %>%
  #used same filter process as last quesiton, this time specifying that race_eth is only showing "white" observations.
  filter(race_eth == "White", race_eth != file_race_black) %>%  
  nrow()


e <- x %>%
  #narrowed table down to just timestamp and their responses
  select(timestamp, response) %>%
  #arranged the timestamp variable and since I selected response, it shows me what the response was for each timestamp. 
  arrange(timestamp)
#Indexed the first and fifth rows which are the first democrat and republican responses ad found the difference between them. 
as.numeric((e$timestamp[1] - e$timestamp[5]) * (-1)) %>%
  round()
```

##Question 1
There were `r a$n` respondents who supported the Democratic candidate.

There were `r b$n[3]-b$n[4]` more respondents who favored the Republican candidate than who were Undecided.

There are two gender variables (gender and gender_combined). There are `r c` individuals for whom these variables have different values.

There are `r d` respondents listed as “White” under race_eth who are not listed as “White” under file_race_black.

The first response of Rep came `r as.numeric((e$timestamp[1] - e$timestamp[5]) * (-1)) %>%
  round()` minutes (rounded to the nearest minute) before the first response of Dem.

##Question 2

```{r make_chart, echo=FALSE, results="asis"}
graphNC <- x %>%
  #Selected the variables needed based on the graph. 
  select(response, race_eth, final_weight) %>%
  
  #Removed the refusals to participate
  filter(race_eth != "[DO NOT READ] Don't know/Refused") %>%
 
  #used this line of code to specify the order of the variables when graphed.
   mutate(race_eth = fct_relevel(race_eth, "White", "Black","Hispanic", "Asian", "Other")) %>% 
  
  #grouped these variables to narrow down our table to what we need
  group_by(response, race_eth) %>%
  
  #created a variable called total which represents the percentage of votes for each party
  summarize(total = sum(final_weight)) %>%
  
  #This moves our table around to show reponse on top and race on the side
  spread(key = response, value= total) %>%
  
  #Narrowed down our table again
  select(race_eth, Dem, Rep, Und) %>% 
 
  #used this to replace NA's with 0's to avoid problems with sums
   replace_na(list(Und = 0)) %>%
  
  #ungrouping is needed to let us start from the beginning with our table
  ungroup() %>%
 
  #created variables to show percentages for dem, rep, and und.
  mutate(all = Dem + Rep + Und) %>% 
  mutate(Dem = Dem / all) %>% 
  mutate(Rep = Rep / all) %>% 
  mutate(Und = Und / all) %>%
  
  #selected our variables needed again because we ungrouped earlier
  select(race_eth, Rep, Dem, Und) %>% 
  
  #begin creating the graph
  gt() %>%
  
  
  #added necessary labels
  tab_header(title = "North Carolina 9th Congressional District Polling Results") %>%
   cols_label(
     race_eth = "Race",
     Dem = "DEM",
      Rep = "REP",
      Und = "UND"
      ) %>%
  
  #turned decimals into percentages
  fmt_percent(columns = vars(Dem, Rep, Und),
                decimals = 0) %>%
  
  #these lines insert a dash instead of a 0 on our graph
  na_if(0) %>%
  fmt_missing(columns = vars(Und), rows = 4)

graphNC
```

##Question 3

```{r, echo = FALSE, warning=FALSE}
GraphNC2 <- x %>%
  #selected variables needed to recreate the graph
  select(educ, final_weight) %>%
  
  #removed the refusals to participate
  filter(educ != "[DO NOT READ] Refused") %>% 
  
  #ordered the table in the same order as the graph provided
  mutate(educ = fct_relevel(educ, "Grade school","High school","Some college or trade school","Bachelors' degree","Graduate or Professional Degree")) %>%
  
  #began creating graph using educ and final_weight as x and y variables repsectively
  ggplot(aes(x = educ, y = final_weight)) +
 
  #selected specific graph used and used geom_jitter to edit the structure of the graph and its data points
  geom_violin() +
  geom_jitter(width = .2, size = 1.0, alpha = .5) + 
  
  #flipped the coordinates so that wording is visible
  coord_flip() +
  
  #added necessary labels
  labs(title= "More Educated Matter Less in North Carolina 9th ",
       subtitle = "Poll gives more weight to people who are less likely to participate in polls",
       caption = "New York Times Upshot/Siena College 2018 live polls") +
  ylab("Weight Given to Respondent in Calculating Poll Results") +
 
  #removed label to match graph provided
  xlab(NULL)

GraphNC2
```

##Question 4
```{r, echo=FALSE, warning=FALSE}
graphNC3 <- x %>%
  #decided to use gender and educ to see if there is a relationship between the education levels of men and women.I made this choice because I am wondering if voters tend to appreciate education levels in women more than men.
  group_by(gender, educ) %>%
  
  #removed the refusals to participate
  filter(educ != "[DO NOT READ] Refused") %>%
  
  #created number of people for each education level by gender
  summarize(total = n()) %>%
  
  #created graph with educ as x value and total as y. filled with gender to clearly show differences between the two. Dodges2 put the charts next to eachother rather than on top of one another
  ggplot(aes( x= educ, y = total, fill = gender)) +
  geom_col(position = "dodge2") +
  
  #added necessary labels
  labs( x = "Education Levels", y = "Number of People") +
  
  #flipped the x and y coordinates so that the education levels label was readable 
  coord_flip()
  
  


  
  
  
graphNC3  
```

##Colleagues
Adiya Abdilkhay;
Alexandra Dobbins;
Albert Shin;
Jenny Li;
Henry Xhu;
Neil Khurana;
Tate Green;
Charlie Flood;
Chris Onesti;
Seeam Noor
  


